### 2021-10-30 manuscript/hiv-gwas.tex
Update on Overleaf.

\documentclass[]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{bm} % for bold math characters
\usepackage{booktabs} % for prettier hlines in table
\usepackage{subcaption} % for subfigures
\usepackage[affil-it]{authblk} % for footnote-style author affiliation
\usepackage{setspace} % for 1.5-spaced lines not including footnotes, floats
\usepackage{tikz} % for graphical model drawing
\usepackage{float} % to enforce figure positioning in subsection they're declared in
\usepackage{amsmath}
\usepackage{longtable} % for table that spans multiple pages
\usepackage[singlelinecheck=false]{caption} % to left-justify single-line table captions

@@

We compared our proposed GWAS framework with a more standard approach by performing two different GWAS on the same SHCS human genotypes. In the ``GWAS with standard trait value'' we used the unmodified trait value, our calculated spVL values, as the GWAS response variable. In the ``GWAS with estimated non-pathogen part of trait'' we used our estimates for the non-pathogen effects on spVL. Figure \ref{fig:gwas-results}A shows that results are qualitatively similar between the two GWAS. Q-Q plots show the distribution of p-values are very similar as well (figure \ref{fig:qq-plots}). Figure \ref{fig:gwas-results}B shows how the strength of association changed for some variants in the MHC and \emph{CCR5} regions. Taking into account phylogenetic information slightly decreased association strength for most variants in \emph{CCR5} region. Association strength increased for some variants in the MHC, for example, SNP rs9265880 had the greatest increase in significance from a p-value of 2.2x10$^{-5}$ to 6x10$^{-7}$. % TODO
However, the two top-associated SNPs are consistent between our study and \cite{McLaren2015} (table \ref{tab:comp-gwas}). In summary, there are no clear patterns that point to new regions of association in the human genome with spVL when we take into account the pathogen phylogeny.

@@

\begin{table}[H]
	\begin{center}
		\begin{tabular}{p{1cm}p{2cm}p{2.5cm}p{1cm}p{2cm}p{1cm}p{2cm}} % {lrrrrrr} {llclcccc}
			\hline
			& & McLaren et al.  & \multicolumn{2}{l}{Standard GWAS } & \multicolumn{2}{l}{GWAS with phylogenetic correction} \\ 
			\hline
			Region & Variant & p-value & Beta & p-value & Beta & p-value \\
			\hline
			MHC & rs59440261 & 2.0 x 10$^{-83}$ & -0.414 & 1.6x10$^{-11}$ & -0.229 & 1.2x10$^{-10}$ \\
			\emph{CCR5} & rs1015164 & 1.5 x 10$^{-19}$ & 0.148 & 1.3x10$^{-6}$ & 0.073 & 3.2x10$^{-5}$ \\			
			\hline
		\end{tabular}
		\caption{Top association results from \cite{McLaren2015} compared to association results in the current study.}
		\label{tab:comp-gwas}
	\end{center}
\end{table}

@@

\begin{longtable}[H]{lp{1cm}p{2cm}p{1cm}p{2cm}p{1cm}p{2cm}} % {lrrrrrr}{lrrrrrr}
		\caption{Association results for common class I HLA alleles ranked by p-value from the GWAS by \cite{McLaren2015} compared to results from the current study.}
		\hline
		& \multicolumn{2}{l}{McLaren et al.}  & \multicolumn{2}{l}{Standard GWAS} & \multicolumn{2}{l}{GWAS with phylogenetic correction} \\ 
		\hline
	 	Allele & Beta & p-value & Beta &p-value & Beta& p-value \\ 
		\hline
		HLA-B*57:01 & -0.840 & $2.69 \times 10^{-86}$ & -0.479 & $1.11 \times 10^{-12}$ & -0.268 & $5.43 \times 10^{-12}$ \\ 
		HLA-C*06:02 & -0.436 & $7.32 \times 10^{-50}$ & -0.173 & $1.10 \times 10^{-4}$ & -0.107 & $3.15 \times 10^{-5}$ \\ 
		HLA-B*27:05 & -0.417 & $4.32 \times 10^{-20}$ & -0.244 & $9.59 \times 10^{-4}$ & -0.122 & $4.40 \times 10^{-3}$ \\ 
		HLA-C*07:01 & 0.195 & $1.86 \times 10^{-14}$ & 0.129 & $7.55 \times 10^{-3}$ & 0.086 & $1.99 \times 10^{-3}$ \\ 
		HLA-C*07:02 & 0.194 & $3.75 \times 10^{-13}$ & 0.095 & $3.02 \times 10^{-2}$ & 0.052 & $3.98 \times 10^{-2}$ \\ 
		HLA-B*07:02 & 0.200 & $5.17 \times 10^{-13}$ & 0.129 & $5.29 \times 10^{-3}$ & 0.072 & $7.06 \times 10^{-3}$ \\ 
		HLA-B*08:01 & 0.206 & $2.94 \times 10^{-11}$ & -0.009 & $9.20 \times 10^{-1}$ & 0.015 & $7.75 \times 10^{-1}$ \\ 
		HLA-C*08:02 & -0.307 & $8.76 \times 10^{-11}$ & 0.324 & $8.55 \times 10^{-1}$ & 0.400 & $6.95 \times 10^{-1}$ \\ 
		HLA-C*04:01 & 0.183 & $9.07 \times 10^{-11}$ & 0.124 & $3.04 \times 10^{-3}$ & 0.058 & $1.67 \times 10^{-2}$ \\ 
		HLA-B*13:02 & -0.346 & $3.70 \times 10^{-10}$ & -0.188 & $1.03 \times 10^{-2}$ & -0.112 & $7.90 \times 10^{-3}$ \\ 
		HLA-B*14:02 & -0.318 & $2.10 \times 10^{-9}$ & 0.067 & $8.12 \times 10^{-1}$ & 0.118 & $4.71 \times 10^{-1}$ \\ 
		HLA-C*12:02 & -0.478 & $4.02 \times 10^{-8}$ & 0.111 & $7.63 \times 10^{-1}$ & 0.094 & $6.58 \times 10^{-1}$ \\ 
		HLA-C*02:02 & -0.223 & $5.45 \times 10^{-8}$ & -0.089 & $1.31 \times 10^{-1}$ & -0.039 & $2.50 \times 10^{-1}$ \\ 
		HLA-A*25:01 & -0.301 & $6.80 \times 10^{-8}$ & -0.090 & $9.93 \times 10^{-2}$ & -0.033 & $2.96 \times 10^{-1}$ \\ 
		HLA-B*52:01 & -0.435 & $2.60 \times 10^{-7}$ & 0.238 & $7.63 \times 10^{-2}$ & 0.150 & $5.33 \times 10^{-2}$ \\ 
		HLA-C*01:02 & -0.231 & $2.22 \times 10^{-6}$ & -0.198 & $5.07 \times 10^{-4}$ & -0.113 & $5.70 \times 10^{-4}$ \\ 
		HLA-A*23:01 & 0.269 & $1.66 \times 10^{-5}$ & 0.020 & $7.42 \times 10^{-1}$ & 0.015 & $6.59 \times 10^{-1}$ \\ 
		HLA-B*55:01 & 0.302 & $2.32 \times 10^{-5}$ & 0.685 & $2.48 \times 10^{-1}$ & 0.436 & $2.03 \times 10^{-1}$ \\ 
		HLA-B*35:02 & 0.358 & $2.42 \times 10^{-5}$ &  &  &  &  \\ 
		HLA-A*31:01 & -0.219 & $4.36 \times 10^{-5}$ & -0.052 & $4.50 \times 10^{-1}$ & -0.017 & $6.78 \times 10^{-1}$ \\ 
		HLA-B*35:01 & 0.156 & $4.82 \times 10^{-5}$ & 0.167 & $2.13 \times 10^{-4}$ & 0.083 & $1.33 \times 10^{-3}$ \\ 
		HLA-B*49:01 & 0.253 & $1.86 \times 10^{-4}$ & 2.173 & $9.79 \times 10^{-4}$ & 1.253 & $9.82 \times 10^{-4}$ \\ 
		HLA-B*35:03 & 0.215 & $7.13 \times 10^{-4}$ & -0.241 & $8.00 \times 10^{-1}$ & 0.261 & $6.35 \times 10^{-1}$ \\ 
		HLA-B*40:01 & 0.148 & $9.37 \times 10^{-4}$ & 0.519 & $1.06 \times 10^{-2}$ & 0.349 & $2.91 \times 10^{-3}$ \\ 
		HLA-B*18:01 & 0.136 & $9.48 \times 10^{-4}$ & 0.208 & $1.73 \times 10^{-3}$ & 0.133 & $5.09 \times 10^{-4}$ \\ 
		HLA-A*29:02 & 0.167 & $1.40 \times 10^{-3}$ & 0.150 & $6.17 \times 10^{-2}$ & 0.092 & $4.72 \times 10^{-2}$ \\ 
		HLA-C*14:02 & -0.228 & $1.50 \times 10^{-3}$ & 0.266 & $7.59 \times 10^{-1}$ & 0.235 & $6.38 \times 10^{-1}$ \\ 
		HLA-A*11:01 & -0.109 & $2.70 \times 10^{-3}$ & -0.090 & $8.96 \times 10^{-2}$ & -0.052 & $8.92 \times 10^{-2}$ \\ 
		HLA-A*24:02 & 0.094 & $3.60 \times 10^{-3}$ & 0.133 & $3.79 \times 10^{-3}$ & 0.074 & $5.52 \times 10^{-3}$ \\ 
		HLA-B*37:01 & 0.222 & $4.50 \times 10^{-3}$ & 0.600 & $3.22 \times 10^{-3}$ & 0.311 & $8.11 \times 10^{-3}$ \\ 
		HLA-B*44:03 & 0.119 & $5.00 \times 10^{-3}$ & -0.114 & $2.77 \times 10^{-1}$ & -0.080 & $1.88 \times 10^{-1}$ \\ 
		HLA-C*03:03 & 0.110 & $6.50 \times 10^{-3}$ & -0.078 & $1.86 \times 10^{-1}$ & -0.031 & $3.66 \times 10^{-1}$ \\ 
		HLA-B*58:01 & -0.253 & $7.10 \times 10^{-3}$ & 6.895 & $7.93 \times 10^{-2}$ & 4.841 & $3.27 \times 10^{-2}$ \\ 
		HLA-A*32:01 & -0.123 & $8.30 \times 10^{-3}$ & 0.089 & $5.31 \times 10^{-1}$ & 0.071 & $3.86 \times 10^{-1}$ \\ 
		HLA-C*16:01 & 0.137 & $8.60 \times 10^{-3}$ & 0.057 & $4.46 \times 10^{-1}$ & 0.013 & $7.60 \times 10^{-1}$ \\ 
		HLA-C*03:04 & 0.093 & $1.25 \times 10^{-2}$ & 0.126 & $3.52 \times 10^{-2}$ & 0.095 & $5.77 \times 10^{-3}$ \\ 
		HLA-B*38:01 & -0.148 & $1.35 \times 10^{-2}$ & -3.459 & $3.01 \times 10^{-1}$ & -2.224 & $2.49 \times 10^{-1}$ \\ 
		HLA-A*33:01 & -0.233 & $1.45 \times 10^{-2}$ &  &  &  &  \\ 
		HLA-A*30:01 & -0.159 & $2.89 \times 10^{-2}$ & 0.072 & $9.04 \times 10^{-1}$ & 0.008 & $9.82 \times 10^{-1}$ \\ 
		HLA-C*12:03 & -0.077 & $4.59 \times 10^{-2}$ & -0.114 & $2.95 \times 10^{-2}$ & -0.067 & $2.68 \times 10^{-2}$ \\ 
		HLA-A*01:01 & 0.051 & $4.78 \times 10^{-2}$ & -0.039 & $4.88 \times 10^{-1}$ & -0.050 & $1.24 \times 10^{-1}$ \\ 
		HLA-B*14:01 & -0.187 & $5.51 \times 10^{-2}$ & 7.071 & $5.00 \times 10^{-2}$ & 3.974 & $5.62 \times 10^{-2}$ \\ 
		HLA-B*40:02 & -0.130 & $1.01 \times 10^{-1}$ & -0.343 & $3.88 \times 10^{-1}$ & -0.105 & $6.47 \times 10^{-1}$ \\ 
		HLA-C*07:04 & 0.125 & $1.02 \times 10^{-1}$ & 0.111 & $3.00 \times 10^{-1}$ & 0.080 & $1.98 \times 10^{-1}$ \\ 
		HLA-C*05:01 & 0.043 & $1.93 \times 10^{-1}$ & -0.022 & $6.51 \times 10^{-1}$ & -0.019 & $4.82 \times 10^{-1}$ \\ 
		HLA-A*03:01 & 0.025 & $3.29 \times 10^{-1}$ & 0.002 & $9.51 \times 10^{-1}$ & -0.001 & $9.81 \times 10^{-1}$ \\ 
		HLA-B*51:01 & -0.036 & $3.52 \times 10^{-1}$ & -0.046 & $3.13 \times 10^{-1}$ & -0.044 & $1.01 \times 10^{-1}$ \\ 
		HLA-A*68:01 & 0.046 & $3.71 \times 10^{-1}$ & 0.036 & $6.09 \times 10^{-1}$ & 0.009 & $8.27 \times 10^{-1}$ \\ 
		HLA-B*44:02 & 0.030 & $3.73 \times 10^{-1}$ & -0.051 & $3.90 \times 10^{-1}$ & -0.031 & $3.57 \times 10^{-1}$ \\ 
		HLA-B*39:01 & 0.073 & $3.85 \times 10^{-1}$ &  &  &  &  \\ 
		HLA-A*02:01 & 0.017 & $3.94 \times 10^{-1}$ & -0.018 & $5.57 \times 10^{-1}$ & -0.008 & $6.77 \times 10^{-1}$ \\ 
		HLA-C*15:02 & -0.046 & $4.20 \times 10^{-1}$ & 0.064 & $3.26 \times 10^{-1}$ & 0.033 & $3.78 \times 10^{-1}$ \\ 
		HLA-B*50:01 & 0.066 & $4.68 \times 10^{-1}$ & 1.522 & $1.77 \times 10^{-2}$ & 0.970 & $8.73 \times 10^{-3}$ \\ 
		HLA-B*15:01 & -0.021 & $5.71 \times 10^{-1}$ & -0.073 & $1.71 \times 10^{-1}$ & -0.021 & $4.93 \times 10^{-1}$ \\ 
		HLA-A*30:02 & 0.050 & $5.92 \times 10^{-1}$ & 0.047 & $9.28 \times 10^{-1}$ & -0.004 & $9.89 \times 10^{-1}$ \\ 
		HLA-A*26:01 & -0.003 & $9.57 \times 10^{-1}$ & -0.645 & $1.96 \times 10^{-1}$ & -0.529 & $6.59 \times 10^{-2}$ \\
		\hline
		\label{tab:full-mclaren-comparison}
\end{longtable}

>>>>

\documentclass[]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{bm} % for bold math characters
\usepackage{booktabs} % for prettier hlines in table
\usepackage{subcaption} % for subfigures
\usepackage[affil-it]{authblk} % for footnote-style author affiliation
\usepackage{setspace} % for 1.5-spaced lines not including footnotes, floats
\usepackage{tikz} % for graphical model drawing
\usepackage{float} % to enforce figure positioning in subsection they're declared in
\usepackage{amsmath}
\usepackage{longtable} % for table that spans multiple pages
\usepackage[singlelinecheck=false]{caption} % to left-justify single-line table captions
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}} % for centered, width-specified columns

@@

We compared our proposed GWAS framework with a more standard approach by performing two different GWAS on the same SHCS human genotypes. In the ``GWAS with standard trait value'' we used the unmodified trait value, our calculated spVL values, as the GWAS response variable. In the ``GWAS with estimated non-pathogen part of trait'' we used our estimates for the non-pathogen effects on spVL. Figure \ref{fig:gwas-results}A shows that results are qualitatively similar between the two GWAS. Q-Q plots show the distribution of p-values are very similar as well (figure \ref{fig:qq-plots}). Figure \ref{fig:gwas-results}B shows how the strength of association changed for some variants in the MHC and \emph{CCR5} regions. Taking into account phylogenetic information slightly decreased association strength for most variants in \emph{CCR5} region. Association strength increased for some variants in the MHC, for example, SNP rs9265880 had the greatest increase in significance in the MHC region, from a p-value of $3.5 \times 10^{-07}$ to $7.7 \times 10^{-09}$. However, the top-associated variants in the MHC and \emph{CCR5} regions were consistent regardless of the GWAS response variable used \ref{tab:gwas-top-associations}. For comparison, table \ref{tab:comp-gwas-mclaren-snps} shows our GWAS results for the two top-associated SNPs identified by \cite{McLaren2015}. In summary, there are no clear patterns that point to new regions of association in the human genome with spVL when we take into account the pathogen phylogeny.

@@

\begin{table}[H]
\centering
\caption{Top association results from \cite{McLaren2015} compared to results from this study from GWAS with unmodified (standard) spVL values and with our estimates for the non-pathogen effects on spVL.}
\begin{tabular}{p{1cm}p{1.8cm}p{2.4cm}p{1.7cm}p{1.8cm}p{1.7cm}p{1.8cm}} % {lrrrrrr} {llclcccc}
\hline
& & McLaren et al.  & \multicolumn{2}{l}{Standard trait value} & \multicolumn{2}{l}{Estimated non-pathogen part of trait} \\ 
  \hline
 Region & Variant & p-value & Effect size & p-value & Effect size & p-value \\
  \hline
    MHC & rs59440261 & $2.0 \times 10^{-83}$ & -0.4 & $3.3 \times 10^{-11}$ & -0.22 & $2.6 \times 10^{-10}$ \\ 
    \emph{CCR5} & rs1015164 & $1.5 \times 10^{-19}$ & 0.15 & $7.5 \times 10^{-7}$ & 0.078 & $8.5 \times 10^{-6}$ \\ 
   \hline
\end{tabular}
\label{tab:comp-gwas-mclaren-snps}
\end{table}

@@

% latex table generated in R 4.1.1 by xtable 1.8-4 package
% Sat Oct 30 10:31:16 2021
\begin{table}[ht]
\caption{Effect size and p-values from top-associated variants in the $\emph{CCR5}$ and MCR regions from the two GWAS performed in our study. ``Standard'' means the GWAS with standard spVL trait values and ``Corrected'' means the GWAS with estimated non-pathogen effects on spVL.}
\begin{tabular}{lllP{2.2cm}P{2.2cm}P{1.6cm}P{2.2cm}}
  \hline
    Region & Position & Variant & Standard effect size & Standard p-value & Corrected effect size & Corrected p-value \\ 
  \hline
    $\emph{CCR5}$ & 46531144 & rs9845968 & -0.16 & $5.6 \times 10^{-9}$ & -0.083 & $1.2 \times 10^{-7}$ \\ 
    $\emph{CCR5}$ & 46537849 & rs867620 & -0.16 & $3.2 \times 10^{-9}$ & -0.085 & $6 \times 10^{-8}$ \\ 
    $\emph{CCR5}$ & 46539864 & rs11130092 & -0.16 & $1.1 \times 10^{-9}$ & -0.087 & $2.6 \times 10^{-8}$ \\ 
    $\emph{CCR5}$ & 46540932 & rs10865942 & -0.16 & $8.4 \times 10^{-9}$ & -0.081 & $4 \times 10^{-7}$ \\ 
    $\emph{CCR5}$ & 46541147 & rs7430431 & -0.17 & $9.2 \times 10^{-10}$ & -0.088 & $2.3 \times 10^{-8}$ \\ 
    MHC & 31274380 & rs9264942 & -0.21 & $4.5 \times 10^{-13}$ & -0.12 & $3.7 \times 10^{-13}$ \\ 
    MHC & 31321919 & rs1055821 & -0.33 & $9.4 \times 10^{-13}$ & -0.19 & $1.4 \times 10^{-12}$ \\ 
    MHC & 31380034 & rs112243036 & -0.32 & $9.9 \times 10^{-16}$ & -0.17 & $3.7 \times 10^{-14}$ \\ 
    MHC & 31391401 & rs4418214 & -0.34 & $2.4 \times 10^{-14}$ & -0.18 & $2.5 \times 10^{-12}$ \\ 
    MHC & 31400137 & rs138130755 & -0.46 & $1 \times 10^{-12}$ & -0.26 & $2.6 \times 10^{-12}$ \\ 
    MHC & 31400705 & rs138117378 & -0.46 & $1 \times 10^{-12}$ & -0.26 & $2.6 \times 10^{-12}$ \\ 
    MHC & 31402358 & rs148792134 & -0.46 & $1 \times 10^{-12}$ & -0.26 & $2.6 \times 10^{-12}$ \\ 
    MHC & 31409677 & rs140991764 & -0.46 & $1 \times 10^{-12}$ & -0.26 & $2.6 \times 10^{-12}$ \\ 
    $\emph{CCR5}$ & 46531144 & rs9845968 & -0.16 & $5.6 \times 10^{-9}$ & -0.083 & $1.2 \times 10^{-7}$ \\ 
    $\emph{CCR5}$ & 46537849 & rs867620 & -0.16 & $3.2 \times 10^{-9}$ & -0.085 & $6 \times 10^{-8}$ \\ 
    $\emph{CCR5}$ & 46539864 & rs11130092 & -0.16 & $1.1 \times 10^{-9}$ & -0.087 & $2.6 \times 10^{-8}$ \\ 
    $\emph{CCR5}$ & 46541147 & rs7430431 & -0.17 & $9.2 \times 10^{-10}$ & -0.088 & $2.3 \times 10^{-8}$ \\ 
    $\emph{CCR5}$ & 46556835 & rs6808142 & 0.15 & $8.3 \times 10^{-8}$ & 0.082 & $3.3 \times 10^{-7}$ \\ 
    MHC & 31274380 & rs9264942 & -0.21 & $4.5 \times 10^{-13}$ & -0.12 & $3.7 \times 10^{-13}$ \\ 
    MHC & 31321919 & rs1055821 & -0.33 & $9.4 \times 10^{-13}$ & -0.19 & $1.4 \times 10^{-12}$ \\ 
    MHC & 31367874 & rs111281598 & -0.37 & $1.5 \times 10^{-12}$ & -0.22 & $2.1 \times 10^{-12}$ \\ 
    MHC & 31376266 & rs73400361 & -0.37 & $1.4 \times 10^{-12}$ & -0.22 & $2.1 \times 10^{-12}$ \\ 
    MHC & 31380034 & rs112243036 & -0.32 & $9.9 \times 10^{-16}$ & -0.17 & $3.7 \times 10^{-14}$ \\ 
   \hline
\end{tabular}
\label{gwas-top-associations}
\end{table}

% \begin{longtable}[H]{lp{1cm}p{2cm}p{1cm}p{2cm}p{1cm}p{2cm}} % {lrrrrrr}{lrrrrrr}
% 		\caption{Association results for common class I HLA alleles ranked by p-value from the GWAS by \cite{McLaren2015} compared to results from the current study.}
% 		\hline
% 		& \multicolumn{2}{l}{McLaren et al.}  & \multicolumn{2}{l}{Standard GWAS} & \multicolumn{2}{l}{GWAS with phylogenetic correction} \\ 
% 		\hline
% 	 	Allele & Beta & p-value & Beta &p-value & Beta& p-value \\ 
% 		\hline
% 		HLA-B*57:01 & -0.840 & $2.69 \times 10^{-86}$ & -0.479 & $1.11 \times 10^{-12}$ & -0.268 & $5.43 \times 10^{-12}$ \\ 
% 		HLA-C*06:02 & -0.436 & $7.32 \times 10^{-50}$ & -0.173 & $1.10 \times 10^{-4}$ & -0.107 & $3.15 \times 10^{-5}$ \\ 
% 		HLA-B*27:05 & -0.417 & $4.32 \times 10^{-20}$ & -0.244 & $9.59 \times 10^{-4}$ & -0.122 & $4.40 \times 10^{-3}$ \\ 
% 		HLA-C*07:01 & 0.195 & $1.86 \times 10^{-14}$ & 0.129 & $7.55 \times 10^{-3}$ & 0.086 & $1.99 \times 10^{-3}$ \\ 
% 		HLA-C*07:02 & 0.194 & $3.75 \times 10^{-13}$ & 0.095 & $3.02 \times 10^{-2}$ & 0.052 & $3.98 \times 10^{-2}$ \\ 
% 		HLA-B*07:02 & 0.200 & $5.17 \times 10^{-13}$ & 0.129 & $5.29 \times 10^{-3}$ & 0.072 & $7.06 \times 10^{-3}$ \\ 
% 		HLA-B*08:01 & 0.206 & $2.94 \times 10^{-11}$ & -0.009 & $9.20 \times 10^{-1}$ & 0.015 & $7.75 \times 10^{-1}$ \\ 
% 		HLA-C*08:02 & -0.307 & $8.76 \times 10^{-11}$ & 0.324 & $8.55 \times 10^{-1}$ & 0.400 & $6.95 \times 10^{-1}$ \\ 
% 		HLA-C*04:01 & 0.183 & $9.07 \times 10^{-11}$ & 0.124 & $3.04 \times 10^{-3}$ & 0.058 & $1.67 \times 10^{-2}$ \\ 
% 		HLA-B*13:02 & -0.346 & $3.70 \times 10^{-10}$ & -0.188 & $1.03 \times 10^{-2}$ & -0.112 & $7.90 \times 10^{-3}$ \\ 
% 		HLA-B*14:02 & -0.318 & $2.10 \times 10^{-9}$ & 0.067 & $8.12 \times 10^{-1}$ & 0.118 & $4.71 \times 10^{-1}$ \\ 
% 		HLA-C*12:02 & -0.478 & $4.02 \times 10^{-8}$ & 0.111 & $7.63 \times 10^{-1}$ & 0.094 & $6.58 \times 10^{-1}$ \\ 
% 		HLA-C*02:02 & -0.223 & $5.45 \times 10^{-8}$ & -0.089 & $1.31 \times 10^{-1}$ & -0.039 & $2.50 \times 10^{-1}$ \\ 
% 		HLA-A*25:01 & -0.301 & $6.80 \times 10^{-8}$ & -0.090 & $9.93 \times 10^{-2}$ & -0.033 & $2.96 \times 10^{-1}$ \\ 
% 		HLA-B*52:01 & -0.435 & $2.60 \times 10^{-7}$ & 0.238 & $7.63 \times 10^{-2}$ & 0.150 & $5.33 \times 10^{-2}$ \\ 
% 		HLA-C*01:02 & -0.231 & $2.22 \times 10^{-6}$ & -0.198 & $5.07 \times 10^{-4}$ & -0.113 & $5.70 \times 10^{-4}$ \\ 
% 		HLA-A*23:01 & 0.269 & $1.66 \times 10^{-5}$ & 0.020 & $7.42 \times 10^{-1}$ & 0.015 & $6.59 \times 10^{-1}$ \\ 
% 		HLA-B*55:01 & 0.302 & $2.32 \times 10^{-5}$ & 0.685 & $2.48 \times 10^{-1}$ & 0.436 & $2.03 \times 10^{-1}$ \\ 
% 		HLA-B*35:02 & 0.358 & $2.42 \times 10^{-5}$ &  &  &  &  \\ 
% 		HLA-A*31:01 & -0.219 & $4.36 \times 10^{-5}$ & -0.052 & $4.50 \times 10^{-1}$ & -0.017 & $6.78 \times 10^{-1}$ \\ 
% 		HLA-B*35:01 & 0.156 & $4.82 \times 10^{-5}$ & 0.167 & $2.13 \times 10^{-4}$ & 0.083 & $1.33 \times 10^{-3}$ \\ 
% 		HLA-B*49:01 & 0.253 & $1.86 \times 10^{-4}$ & 2.173 & $9.79 \times 10^{-4}$ & 1.253 & $9.82 \times 10^{-4}$ \\ 
% 		HLA-B*35:03 & 0.215 & $7.13 \times 10^{-4}$ & -0.241 & $8.00 \times 10^{-1}$ & 0.261 & $6.35 \times 10^{-1}$ \\ 
% 		HLA-B*40:01 & 0.148 & $9.37 \times 10^{-4}$ & 0.519 & $1.06 \times 10^{-2}$ & 0.349 & $2.91 \times 10^{-3}$ \\ 
% 		HLA-B*18:01 & 0.136 & $9.48 \times 10^{-4}$ & 0.208 & $1.73 \times 10^{-3}$ & 0.133 & $5.09 \times 10^{-4}$ \\ 
% 		HLA-A*29:02 & 0.167 & $1.40 \times 10^{-3}$ & 0.150 & $6.17 \times 10^{-2}$ & 0.092 & $4.72 \times 10^{-2}$ \\ 
% 		HLA-C*14:02 & -0.228 & $1.50 \times 10^{-3}$ & 0.266 & $7.59 \times 10^{-1}$ & 0.235 & $6.38 \times 10^{-1}$ \\ 
% 		HLA-A*11:01 & -0.109 & $2.70 \times 10^{-3}$ & -0.090 & $8.96 \times 10^{-2}$ & -0.052 & $8.92 \times 10^{-2}$ \\ 
% 		HLA-A*24:02 & 0.094 & $3.60 \times 10^{-3}$ & 0.133 & $3.79 \times 10^{-3}$ & 0.074 & $5.52 \times 10^{-3}$ \\ 
% 		HLA-B*37:01 & 0.222 & $4.50 \times 10^{-3}$ & 0.600 & $3.22 \times 10^{-3}$ & 0.311 & $8.11 \times 10^{-3}$ \\ 
% 		HLA-B*44:03 & 0.119 & $5.00 \times 10^{-3}$ & -0.114 & $2.77 \times 10^{-1}$ & -0.080 & $1.88 \times 10^{-1}$ \\ 
% 		HLA-C*03:03 & 0.110 & $6.50 \times 10^{-3}$ & -0.078 & $1.86 \times 10^{-1}$ & -0.031 & $3.66 \times 10^{-1}$ \\ 
% 		HLA-B*58:01 & -0.253 & $7.10 \times 10^{-3}$ & 6.895 & $7.93 \times 10^{-2}$ & 4.841 & $3.27 \times 10^{-2}$ \\ 
% 		HLA-A*32:01 & -0.123 & $8.30 \times 10^{-3}$ & 0.089 & $5.31 \times 10^{-1}$ & 0.071 & $3.86 \times 10^{-1}$ \\ 
% 		HLA-C*16:01 & 0.137 & $8.60 \times 10^{-3}$ & 0.057 & $4.46 \times 10^{-1}$ & 0.013 & $7.60 \times 10^{-1}$ \\ 
% 		HLA-C*03:04 & 0.093 & $1.25 \times 10^{-2}$ & 0.126 & $3.52 \times 10^{-2}$ & 0.095 & $5.77 \times 10^{-3}$ \\ 
% 		HLA-B*38:01 & -0.148 & $1.35 \times 10^{-2}$ & -3.459 & $3.01 \times 10^{-1}$ & -2.224 & $2.49 \times 10^{-1}$ \\ 
% 		HLA-A*33:01 & -0.233 & $1.45 \times 10^{-2}$ &  &  &  &  \\ 
% 		HLA-A*30:01 & -0.159 & $2.89 \times 10^{-2}$ & 0.072 & $9.04 \times 10^{-1}$ & 0.008 & $9.82 \times 10^{-1}$ \\ 
% 		HLA-C*12:03 & -0.077 & $4.59 \times 10^{-2}$ & -0.114 & $2.95 \times 10^{-2}$ & -0.067 & $2.68 \times 10^{-2}$ \\ 
% 		HLA-A*01:01 & 0.051 & $4.78 \times 10^{-2}$ & -0.039 & $4.88 \times 10^{-1}$ & -0.050 & $1.24 \times 10^{-1}$ \\ 
% 		HLA-B*14:01 & -0.187 & $5.51 \times 10^{-2}$ & 7.071 & $5.00 \times 10^{-2}$ & 3.974 & $5.62 \times 10^{-2}$ \\ 
% 		HLA-B*40:02 & -0.130 & $1.01 \times 10^{-1}$ & -0.343 & $3.88 \times 10^{-1}$ & -0.105 & $6.47 \times 10^{-1}$ \\ 
% 		HLA-C*07:04 & 0.125 & $1.02 \times 10^{-1}$ & 0.111 & $3.00 \times 10^{-1}$ & 0.080 & $1.98 \times 10^{-1}$ \\ 
% 		HLA-C*05:01 & 0.043 & $1.93 \times 10^{-1}$ & -0.022 & $6.51 \times 10^{-1}$ & -0.019 & $4.82 \times 10^{-1}$ \\ 
% 		HLA-A*03:01 & 0.025 & $3.29 \times 10^{-1}$ & 0.002 & $9.51 \times 10^{-1}$ & -0.001 & $9.81 \times 10^{-1}$ \\ 
% 		HLA-B*51:01 & -0.036 & $3.52 \times 10^{-1}$ & -0.046 & $3.13 \times 10^{-1}$ & -0.044 & $1.01 \times 10^{-1}$ \\ 
% 		HLA-A*68:01 & 0.046 & $3.71 \times 10^{-1}$ & 0.036 & $6.09 \times 10^{-1}$ & 0.009 & $8.27 \times 10^{-1}$ \\ 
% 		HLA-B*44:02 & 0.030 & $3.73 \times 10^{-1}$ & -0.051 & $3.90 \times 10^{-1}$ & -0.031 & $3.57 \times 10^{-1}$ \\ 
% 		HLA-B*39:01 & 0.073 & $3.85 \times 10^{-1}$ &  &  &  &  \\ 
% 		HLA-A*02:01 & 0.017 & $3.94 \times 10^{-1}$ & -0.018 & $5.57 \times 10^{-1}$ & -0.008 & $6.77 \times 10^{-1}$ \\ 
% 		HLA-C*15:02 & -0.046 & $4.20 \times 10^{-1}$ & 0.064 & $3.26 \times 10^{-1}$ & 0.033 & $3.78 \times 10^{-1}$ \\ 
% 		HLA-B*50:01 & 0.066 & $4.68 \times 10^{-1}$ & 1.522 & $1.77 \times 10^{-2}$ & 0.970 & $8.73 \times 10^{-3}$ \\ 
% 		HLA-B*15:01 & -0.021 & $5.71 \times 10^{-1}$ & -0.073 & $1.71 \times 10^{-1}$ & -0.021 & $4.93 \times 10^{-1}$ \\ 
% 		HLA-A*30:02 & 0.050 & $5.92 \times 10^{-1}$ & 0.047 & $9.28 \times 10^{-1}$ & -0.004 & $9.89 \times 10^{-1}$ \\ 
% 		HLA-A*26:01 & -0.003 & $9.57 \times 10^{-1}$ & -0.645 & $1.96 \times 10^{-1}$ & -0.529 & $6.59 \times 10^{-2}$ \\
% 		\hline
% 		\label{tab:full-mclaren-comparison}
% \end{longtable}
